Studies of quantum dots

### 2017-01-18 Manuscript/paper.tex
spEnergiesQD/Manuscript/paper.tex: add placeholders

\subsection{Equations of Motion Methods}

@@

@@

Methods exist for transforming the mixed density into the pure density $|\Phi(\bm{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.~for comparisons with other methods), this is strictly not necessary.

@@

\begin{acknowledgments}
  This work was supported by the National Science Foundation Grant No.~PHY-1404159 (Michigan State University) and by the Research Council of Norway under contract ISP-Fysikk/216699.  This research used computational resources of the Notur project in Norway.  We thank Christoffer Hirth, Simen Kvaal and Veronica Olsen for several discussions.
\end{acknowledgments}

>>>>

\subsection{Equations of motion methods}

@@

\subsection{Coupled cluster theory}

[[?]]

\subsubsection{EOM-CC}

[[?]]

@@

Methods exist for transforming the mixed density into the pure density $|\Phi(\bm{r}, \tau)|^2$ \cite{abInitioMC}, but unless the pure density is explicitly needed (e.g.\ for comparisons with other methods), this is strictly not necessary.

@@

\begin{acknowledgments}
  This work was supported by the National Science Foundation Grant No.\ PHY-1404159 (Michigan State University) and by the Research Council of Norway under contract ISP-Fysikk/216699.  This research used computational resources of the Notur project in Norway.  We thank Christoffer Hirth, Simen Kvaal and Veronica Olsen for several discussions.
\end{acknowledgments}
